Network Analysis of Code Similarity

### 2014-11-21 network-analysis.Rmd
Remove anachronistic comparisons

```{r}
cf <- outer_for_lists(codes, codes, compare_codes_by_shared_ngrams)
diag(cf) <- NA   # remove codes compared to themselves
```

>>>>

```{r}
cf <- outer_for_lists(codes, codes, compare_codes_by_shared_ngrams)
diag(cf) <- NA                 # remove codes compared to themselves
cf <- rm_anachronism(cf)       # remove anachronistic comparisons
```
